The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-07-26 albatros_paper.tex
HCC added new version of baseband/direct phase comparison plot

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.jpg}
    \caption{\attention{Placeholder figure} Phases from the
      cross-correlation between two orthogonal polarizations from an
      \albatros\ pathfinder at MARS (see text for details).  The top
      row shows cross-spectrum phases that are accumulated directly by
      the SNAP board, and the bottom row shows phases computed from
      baseband data with 4-bit quantization.  The two frequency
      windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are recorded at two
      separate times, and all waterfall plots are shown with 61-kHz
      resolution.}
    \label{Fig:baseband_direct_phase}
  \end{center}
\end{figure}

>>>>

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.png}
    \caption{Phases from the cross-correlation between two orthogonal
      polarizations from an \albatros\ pathfinder at MARS (see text
      for details).  The top row shows cross-spectrum phases that are
      accumulated directly by the SNAP board, and the bottom row shows
      phases computed from baseband data with 4-bit quantization.  The
      two frequency windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are
      recorded at two separate times, and all waterfall plots are
      shown with 61-kHz resolution.}
    \label{Fig:baseband_direct_phase}
  \end{center}
\end{figure}
